\documentclass{beamer}

\usepackage{amsmath}

\usetheme{Warsaw}

\mode<presentation>

%Information to be included in the title page:
\title{Comparing the Classical and Nonclassical Symmetries of Nonlinear Partial Differential Equations}
\author{William Helman and Daniel Sinderson}
\institute{Southern Oregon University}
\date{2023}

\begin{document}

\frame{\titlepage}



\begin{frame}
    \frametitle{Introduction}
    Our research objective for this project was to calculate the classical and nonclassical symmetry groups for the reduced Gibbons-Tsarev equation and the Born-Infeld equation and compare them.
\end{frame}



\begin{frame}
    \frametitle{What is a symmetry?}
    \framesubtitle{Definitions}
    \begin{definition}<1->
        A symmetry is a transformation that leaves an object invariant.
    \end{definition}

    \begin{definition}<2->
        A symmetry is a change that doesn't change anything.
    \end{definition}
    
\end{frame}

\begin{frame}
    \frametitle{What is a symmetry?}
    \framesubtitle{A Transformation that's not a Symmetry}
    \begin{example}[1]<1->
        Let's take the equation $x-y=0$.
        \\In slope-intercept form, this is the line $y=x$.
        \begin{itemize}
            \item For our first transformation, let's define new variables\\ $\bar{x}=x+1$ and $\bar{y}=y$.
            \item Now we rewrite our equation using these new variables. \begin{equation*}
                \begin{aligned}
                    \bar{x}-\bar{y} &= 0 & \text{by definition} \\
                    x+1-y &= 0 & \text{by substitution} \\
                    y &= x+1 & \text{by rewriting in slope-intercept form}
                \end{aligned}
            \end{equation*}
            \item As we can see, this is NOT a transformation: \\ $x-y+1\ne x-y$
        \end{itemize}        
    \end{example}
\end{frame}


\begin{frame}
    \frametitle{What is a symmetry?}
    \framesubtitle{A Transformation that is a Symmetry}
    \begin{example}[2]<1->
        \begin{itemize}
            \item Let's define some new variables again\\ $\bar{x}=x+1$ and $\bar{y}=y+1$.
            \item Now we rewrite our equation using these new variables. \begin{equation*}
                \begin{aligned}
                    \bar{x}-\bar{y} &= 0 & \text{by definition} \\
                    (x+1)-(y+1) &= 0 & \text{by substitution} \\
                    (x-y)+(1-1) &= 0 & \text{by algebra} \\
                    x-y &= 0 & \text{by algebra} \\
                    y &= x & \text{by rewriting in slope-intercept form}
                \end{aligned}
            \end{equation*}
            \item As we can see, this IS a transformation: \\ $x-y = x-y$
        \end{itemize}        
    \end{example}
\end{frame}




\begin{frame}
    \frametitle{What is a Differential Equation?}

\end{frame}



\begin{frame}
    \frametitle{The History of the Born-Infeld and the reduced Gibbons-Tsarev Equations}

\end{frame}



\begin{frame}
    \frametitle{The Classical Symmetries of the Born-Infeld and the reduced Gibbons-Tsarev Equations}

\end{frame}



\begin{frame}
    \frametitle{The Nonclassical Symmetries of the Born-Infeld and the reduced Gibbons-Tsarev Equations}

\end{frame}



\begin{frame}
    \frametitle{Future Work: Does Integrability Imply Equivalence of Classical and Nonclassical Symmetries?}

\end{frame}



\begin{frame}
    \frametitle{Future Work: Does Equivalence of Classical and Nonclassical Symmetries Imply Integrability?}

\end{frame}



\end{document}